\textbf{{\Large {Recurrent relation for branching coefficients of affine Lie algebras}}}

### 2009-11-06 AffineLieAlgebras/InformalNotes/article.tex
Some work on affine branching

\begin{comment}
  Another examples?
\end{comment}
\subsection{Affine Lie algebras}
\label{sec:affine-lie-algebras}
\begin{comment}
  What examples should we include here?
\end{comment}
\subsubsection{Embedding of finite-dimensional algebra into affine algebra}
\label{sec:embedd-finite-dimens}

@@

>>>>

\subsection{Affine Lie algebras}
\label{sec:affine-lie-algebras}
\subsubsection{Embedding of finite-dimensional algebra into affine algebra}
\label{sec:embedd-finite-dimens}

The maximal embeddings of the finite-dimensional Lie algebras into the affine Lie algebras were thoroughly studied and the tables of the branching coefficients are given in the book \cite{kass1990ala}. The task of the study of non-maximal embeddings is then can be reduced to the well-known task of branching of the finite-dimensional Lie algebras.
Thus here we show the simplest possible example of reduction of affine $\widehat{A_1}$ to $A_1$ in order to demonstrate some traits of our method and show that we eliminate the need of slice-by-slice study discussed in \cite{kass1990ala}.

The simple roots for the affine $\widehat{A_1}$ are
\begin{equation}
  \label{eq:2}
  (\alpha,\delta-\alpha)
\end{equation}
We consider the embedding with the root $\beta=\delta-\alpha$.

Positive roots of the $\widehat{A_1}$ are $\alpha,\; \alpha+n\delta,\; n\delta,\; -\alpha+n\delta;\; n=1,2,3,\dots$.
The set of the

@@

Consider the affine extension of the example \ref{sec:regul-embedd-a_1}. 
Since this embedding is regular, the level of the representations of the subalgebra is equal to the level of the representation of the algebra.

The set $\Delta_{\bot}$ of the orthogonal positive roots with the zero projection on the root space of the subalgebra $\widehat{A_1}$ is the same as in the finite-dimensional case.

Consider the level one representation of the algebra $\mathfrak{g}=\widehat{B_2}$ with the highest weight $(1,0,1,0)$, where the first to components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the grade of the weight and the fourth is the level.

The set of the anomalous points of this representation up to sixth grade is depicted in the figure \ref{fig:affine_B2_anom_point} and in each grade it looks like in the figure \ref{fig:B2_A1}.

\begin{figure}[ph]
  \centering
  \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
  \caption{The anomalous points of the $(1,0,1,0)$ representation of the algebra $\widehat{B_2}$}
  \label{fig:affine_B2_anom_point}
\end{figure}
